### 2019-02-15 manuscript/methods.tex
- something was messed up with references (minimum needed fix; hoehna_2016, soltis_2014 missing fields) - if someone wishes to git remove main.pdf, that would be okay

To those existing data sets, we added some additional records for chromosome number and breeding system.
The Supplementary Information contains citations for the numerous sources for the added data. % todo: add number of refs when we have it
Resolution of taxonomic synonymy followed the conventions provided in Solanaceae Source \citep{solsource}. %B: was Synonymy followed Solanaceae Source \citep{solsource}.
Hybrids and cultivars were excluded because ploidy and breeding system can be affected by artificial selection during domestication. %B: was: Hybrids and cultivars were excluded because ploidy and breeding system are likely to be altered by domestication.
Following the reasoning outlined in \citet{robertson_2011}, we examined closely the few species for which the merged ploidy and breeding system data indicated the presence of self-incompatible polyploids.
Although SI populations frequently contain some SC individuals, and diploid populations frequently contain some polyploid individuals, in no case did we find a convincing case of a naturally occurring SI and polyploid population.
%B: Thus qualified, as above, I think this should be inserted for maximum Truth.
The single instance of an SI and polyploid individual appears to be an allopentaploid hybrid of {\em Solanum oplocense} Hawkes x {\em Solanum gourlayii} Hawkes, reported by \citealt{camadro1981}.

>>>>

To those existing data sets, we added some additional records for chromosome number and breeding system.
The Supplementary Information contains citations for the numerous sources for the added data. % todo: add number of refs when we have it
Resolution of taxonomic synonymy followed the conventions provided in Solanaceae Source \citep{solsource}. %B: was Synonymy followed Solanaceae Source \citep{solsource}.
Hybrids and cultivars were excluded because ploidy and breeding system can be affected by artificial selection during domestication. %B: was: Hybrids and cultivars were excluded because ploidy and breeding system are likely to be altered by domestication.
Following the reasoning outlined in \citet{robertson_2011}, we examined closely the few species for which the merged ploidy and breeding system data indicated the presence of self-incompatible polyploids.
Although SI populations frequently contain some SC individuals, and diploid populations frequently contain some polyploid individuals, in no case did we find a convincing case of a naturally occurring SI and polyploid population.
%B: Thus qualified, as above, I think this should be inserted for maximum Truth.
The single instance of an SI and polyploid individual appears to be an allopentaploid hybrid of {\em Solanum oplocense} Hawkes x {\em Solanum gourlayii} Hawkes, reported by \citealt{camadro_1981}.
